tutorial_notes

### 2024-12-05 notes/tutorial_notes.Rmd
comments on Tutorial 2b

>>>>

# December 5th 2024 #

I took a look at tutorial2b.

## coding conventions ##

I edited stuff to make each code argument after a pipe a new line. 
I think it is easier to read this way.
You can also "re-indent" lines to make the code more consistent in terms of indents also.
e.g., cmd+I or select the tab "code" then "re-indent lines"

## priors ##

line 101. we don't say anything about how we came to set the priors how we did. 
Should we say something? Or do we say it elsewhere?
Maybe a few lines about weakly iformative priors and what that means in this context?

## plots ##

a very minor point.
for the grand average marginal effects, you facet by condition.
for the single subject marginal effects, you overlap the lines.
This is not a big deal, I'm just pointing out the difference.
e.g., you could plot the grand average in the same way. 
I'm not saying that would be better. I'm just saying that it would then be consistent.
It makes no difference overall as they are both very clear as they are.
